\section{\label{sec:summary}Summary of Running Conditions}

This document is organized as follows. Section~\ref{sec:summary} has basic information about the \desg{g12} run, including the physics goals. Section~\ref{sec:calib} describes the calibrations; it is quite long and uses standard \abbr{CLAS} procedures. One item of note is that the beam current was high for \abbr{CLAS}, typically about 60 nA. Of course, the background rate goes quadratically with beam current, and so the \desg{g12} data have more background yet the calibration procedures still work. Section~\ref{sec:data} provides the cooking procedures, as well as the momentum and beam-energy corrections. Since \desg{g12} also had a lepton trigger, Section~\ref{sec:data.lepton} gives additional information relevant to the lepton detection using the CC and EC. Section~\ref{sec:flux} has a straight-forward description of the beam flux, using the \prog{gflux} method with the \verb+–c+ option (clock-based DAQ). Section~\ref{sec:sim} provides the procedures for simulations, including all command-line options (some a1c options are specific to BOS files made from simulations). This section also has specific information for \desg{g12}, such as the fiducial cuts and simulations of the \desg{g12} trigger. Finally, Sections~\ref{sec:resonances} and \ref{sec:xsec} together show that the world data on cross sections for at least two reactions (ω meson production and K$^+$ Λ production) agree well with previously reported world data. This gives us confidence that the calibrations, energy corrections, beam flux and simulations are being done correctly.

The goal of this document is to provide a basis for individual analyses of \desg{g12} data to undergo a shortened analysis review. In other words, if the procedures here are followed also in individual analyses, then the review committees can focus on the cuts and systematics specific to the final state of an individual analysis, with confidence that the calibrations, corrections, etc., have already been reviewed.

The \desg{g12} experiment contained several analyses where the main goal was to search for resonances in the multi-particle final state by performing partial wave analysis. These analyses\cite{clas.thesis.bookwalter, clas.thesis.schott} do not require absolute normalization and therefore several steps discussed below were skipped. For a general discussion of the PWA procedure by \desg{g12} Ref.~\cite{pwa.salgado2014}. We do however provide details for analyses that do want this normalization for cross sections and upper limits later in this document.

The \desg{g12} experiment was a high-luminosity, high-energy real-photon run for \abbr{CLAS}. The electron beam current was 60--65~nA on the 40~cm $\ell$H$_2$ target. A total of $26\times 10^8$ triggers were recorded using several of the 12 available trigger bits. The ``production trigger'' required two prongs (start-counter and time-of-flight coincidence) in two different sectors and in coincidence with a tagger hit at or above 3.6~GeV. There was secondary trigger which required three prongs, again in different sectors, regardless of tagger hits. The running conditions are summarized in Table~\ref{tab:runconditions}. There were three proposals associated with this experiment which are listed here:
\input{summary/proposal_list}
In addition to this document, there is a wealth of information to be found in the wiki pages at
\begin{center}
    \url{http://clasweb.jlab.org/rungroups/g12/wiki}
\end{center}
which has served as a repository for all things related to the \desg{g12} experiment. The dissertations associated with this experiment contain a lot of information as well:

\input{summary/dissertation_list}

\input{tables/runconditions}

\input{summary/trigger}
\input{summary/runlists}
